---
title: "Piperacillin TDM Summary"
output:
  word_document:
    fig_height: 6
    fig_width: 8
---

````{r, echo=FALSE}
setwd(dir)
#reference_docx: mystyles.docx
#Custome ggplot2 theme for the Word document
theme_bw2 <- theme_set(theme_bw(base_size = 16))
theme_bw2 <- theme_update(plot.margin = unit(c(0.5,0.5,0.5,0.5), "lines"),
													axis.title.x=element_text(size = 16, vjust = 0),
													axis.title.y=element_text(size = 16, vjust = 0, angle = 90),
													strip.text.x=element_text(size = 14),
													strip.text.y=element_text(size = 14, angle = 90),
                          legend.direction = "vertical",
                         	legend.position = "bottom",
                         	legend.box = "horizontal")
````
  
# `r paste(paste(input$FNAME,input$LNAME,sep=" "),paste("(URN: ",input$URN,")",sep=""),sep=" ")`
****
  
## Patient and Previous Dosing Details

``` {r, echo=FALSE, warning=FALSE}
#Calculate AGE
AGE <- round(as.double(difftime(input$DDATE,input$BDATE))/365, digits = 1)
#Assign labels to "SEX"
SEX <- NA
if (input$SEX == 1) {SEX <- "Male"}
if (input$SEX == 2) {SEX <- "Female"}
#Find individual's value for CRCL
CRCL <- round(rOBS.data$CRCL[1], digits = 1)
#Assign labels to "PFREQ"
PFREQ <- NA
if (input$PFREQ == 1) {PFREQ <- "4-hourly"}
if (input$PFREQ == 2) {PFREQ <- "6-hourly"}
if (input$PFREQ == 3) {PFREQ <- "8-hourly"}
#Assign labels to "NPDOSE"
NPDOSE <- NA
if (input$NPDOSE == 1) {NPDOSE <- "No previous doses, this was the first dose"}
if (input$NPDOSE == 2) {NPDOSE <- "1"}
if (input$NPDOSE == 3) {NPDOSE <- "2"}
if (input$NPDOSE == 4) {NPDOSE <- "3 or more previous doses (at steady state"}
#Assign labels to "PCONC" and "PTIME"
if (input$NCONC == 1) {
  PCONC1 <- input$PCONC1
  PTIME1 <- input$PTIME1
  PCONC2 <- NA
  PTIME2 <- NA
  PCONC3 <- NA
  PTIME3 <- NA
  PCONC4 <- NA
  PTIME4 <- NA
}
if (input$NCONC == 2) {
  PCONC1 <- input$PCONC1
  PTIME1 <- input$PTIME1
  PCONC2 <- input$PCONC2
  PTIME2 <- input$PTIME2
  PCONC3 <- NA
  PTIME3 <- NA
  PCONC4 <- NA
  PTIME4 <- NA
}
if (input$NCONC == 3) {
  PCONC1 <- input$PCONC1
  PTIME1 <- input$PTIME1
  PCONC2 <- input$PCONC2
  PTIME2 <- input$PTIME2
  PCONC3 <- input$PCONC3
  PTIME3 <- input$PTIME3
  PCONC4 <- NA
  PTIME4 <- NA
}
if (input$NCONC == 4) {
  PCONC1 <- input$PCONC1
  PTIME1 <- input$PTIME1
  PCONC2 <- input$PCONC2
  PTIME2 <- input$PTIME2
  PCONC3 <- input$PCONC3
  PTIME3 <- input$PTIME3
  PCONC4 <- input$PCONC4
  PTIME4 <- input$PTIME4
}
```
  
**Characteristics**                   | **Value**  
------------------------------------- | ----------------------------------------  
Age (years)                           | `r AGE`  
Weight (kg)                           | `r input$WT`  
Gender                                | `r SEX`  
Serum Creatinine (µmol/L)             | `r input$SECR`  
Creatinine Clearance (mL/min)         | `r CRCL`  

**Prescribed Dosing Information**     | **Value**  
------------------------------------- | ----------------------------------------  
Dose Amount (mg)                      | `r input$PDOSE`  
Dose Frequency (hours)                | `r PFREQ`  
Infusion Duration (hours)             | `r input$PINFD`  
Number of Previous Doses              | `r NPDOSE`  

**Concentration (mg/L)**              | **Time after Infusion Started (hours)**   
------------------------------------- | ----------------------------------------    
1: `r PCONC1`                         | `r PTIME1`    
2: `r PCONC2`                         | `r PTIME2`    
3: `r PCONC3`                         | `r PTIME3`    
4: `r PCONC4`                         | `r PTIME4`    

  
## Individual Pharmacokinetic Parameters

``` {r, echo=FALSE, warning=FALSE}
#Individual estimate for CL
iCOVCRCL <- head(rOBS.data$CL,1)
CLi <- round(rBAYES.data$par[1] + iCOVCRCL, digits = 1)
#Individual estimate for V
iCOVWT <- head(rOBS.data$V,1)
Vi <- round(rBAYES.data$par[2] + iCOVWT, digits = 1)
#Confidence intervals
#Calculate standard errors for individual parameter estimates
#Assign the R matrix to the Hessian returned by optim
Rmatrix <- rBAYES.data$hessian
#Calculate the variance-covariance matrix
VCmatrix <- solve(Rmatrix)
#Calculate the parameter standard errors
se.par <- sqrt(diag(VCmatrix))
#Calculate parameter standard errors as a percentage (CL, V)
ERR.CL <- rnorm(n, mean=rBAYES.data$par[1], sd=se.par[1])
ERR.CL <- ERR.CL + iCOVCRCL
CL.low <- round(quantile(ERR.CL, probs=0.025), digits = 1)
CL.hi <- round(quantile(ERR.CL, probs=0.975), digits = 1)
ERR.V <- rnorm(n, mean=rBAYES.data$par[2], sd=se.par[2])
ERR.V <- ERR.V + iCOVWT
V.low <- round(quantile(ERR.V, probs=0.025), digits = 1)
V.hi <- round(quantile(ERR.V, probs=0.975), digits = 1)
#Define individual's estimate for CL (95% CI)
CLfit <- paste(CLi," (",CL.low," - ",CL.hi,")",sep="")
#Define individual's estimate for V (95% CI)
Vfit <- paste(Vi," (",V.low," - ",V.hi,")",sep="")
```
    
**Estimated Parameters**                              | **Value (95% CI)**  
----------------------------------------------------- | -------------------
Clearance (L/hour)                                    | `r CLfit`  
Volume of Distribution (L)                            | `r Vfit`  
Time above MIC for Sampled Dose (%)                   | `r rMIC.data1$Value[1]`  

  
``` {r, echo=FALSE, warning=FALSE}
#Plot
plotobj1 <- NULL
plotobj1 <- ggplot(rFIT.data)
plotobj1 <- plotobj1 + stat_summary(aes(x = TIME, y = IPRE), data = rCI.data1, geom = "ribbon", fun.ymin = CI95lo, fun.ymax = CI95hi, alpha = 0.2)
plotobj1 <- plotobj1 + geom_line(aes(x = TIME, y = IPRE), size = 1, colour = "steelblue3")  #Blue line = bayes estimated
plotobj1 <- plotobj1 + geom_line(aes(x = TIME, y = IPRE), data = rSIM.data1, size = 1, colour = "firebrick3", linetype = "longdash")  #Red line = simulated
#Set up a labelled dashed-line representing the MIC depending on input
#Had to set it up like this because having the SMIC1 object in geom_hline wasn't working
if (input$MIC == 1) {
plotobj1 <- plotobj1 + geom_hline(aes(yintercept = 0.25), linetype = "dashed", colour = "black")
}
if (input$MIC == 2) {
plotobj1 <- plotobj1 + geom_hline(aes(yintercept = 0.5), linetype = "dashed", colour = "black")
}
if (input$MIC == 3) {
plotobj1 <- plotobj1 + geom_hline(aes(yintercept = 1), linetype = "dashed", colour = "black")
}
if (input$MIC == 4) {
plotobj1 <- plotobj1 + geom_hline(aes(yintercept = 2), linetype = "dashed", colour = "black")
}
if (input$MIC == 5) {
plotobj1 <- plotobj1 + geom_hline(aes(yintercept = 4), linetype = "dashed", colour = "black")
}
if (input$MIC == 6) {
plotobj1 <- plotobj1 + geom_hline(aes(yintercept = 8), linetype = "dashed", colour = "black")
}
if (input$MIC == 7) {
plotobj1 <- plotobj1 + geom_hline(aes(yintercept = 16), linetype = "dashed", colour = "black")
}
if (input$MIC == 8) {
plotobj1 <- plotobj1 + geom_hline(aes(yintercept = 32), linetype = "dashed", colour = "black")
}
if (input$MIC == 9) {
plotobj1 <- plotobj1 + geom_hline(aes(yintercept = 64), linetype = "dashed", colour = "black")
}
plotobj1 <- plotobj1 + geom_point(aes(x = TIME, y = DV), size = 4)  #Black circles = observed data used to estimate
plotobj1 <- plotobj1 + scale_x_continuous("\nTime (hours)")
plotobj1 <- plotobj1 + scale_y_continuous("Piperacillin Concentration (mg/L)\n")
print(plotobj1)
```
  
## Recommended Dosing Regimen   
  
```{r, echo=FALSE, warning=FALSE}
SFREQ1 <- NA
if (input$SFREQ1 == 1) {SFREQ1 <- "4-hourly"}
if (input$SFREQ1 == 2) {SFREQ1 <- "6-hourly"}
if (input$SFREQ1 == 3) {SFREQ1 <- "8-hourly"}
```
  
**New Dosing Information**                           | **Value**  
---------------------------------------------------- | ---------------------
Dose Amount (mg)                                     | `r input$SDOSE1`  
Dose Frequency (hours)                               | `r SFREQ1`  
Infusion Duration (hours)                            | `r input$SINFD1`  

**Predictions**                                      | **Value (95% CI)**  
---------------------------------------------------- | ---------------------
Time above MIC for Next 3 Doses (%)                  | `r rMIC.data1$Value[2]`  

  
> *[Type your overall dosing recommendations here]*  
  
****
  
**Prepared by:** `r input$PHARMI` (Pharmacist) **Date:** `r format(Sys.Date(), "%d-%m-%Y")`
